Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-07-31 pirouette_supplement.tex
Changes @rsetienne

Based on the 'twin alignment' (center-right panel), the candidate model
with the highest marginal likelihood is determined, from the same 
set of 15 candidate models.The inference model that had the
highest evidence (as shown in Table \ref{tab:evidence_twin}) was 
the inference model with a JC nucleotide substitution model,
an RLN clock model and a Yule tree model 
\new{
  (note: this mismatches how
  the twin tree and twin tree were simulated, as the twin tree
  is generated using a BD process, where the alignment
  is simulated using a JC substitution model and strict clock model
  ).
}
From the 'twin alignment' this best candidate inference model is run.
The resulting posterior trees are shown in the fourth panel
of the third row of posteriors in figure \ref{fig:pipeline}.

@@

From the names of the estimated parameters, it is clear that
the best candidate model for the twin tree
is JC nucleotide substitution 
model (no parameter needed to be estimated),
an RLN clock model (which can be inferred from the parameter 'rate.mean') 
and a Yule model ('YuleModel', 'birthRate').
Note that there is a mismatch between the actual process of how the twin tree
and twin alignment are generated, as the twin tree is generated by a
BD process, and the alignment is simulated using a JC nucleotide
substitution model and a strict clock model.

@@

The marginal likelihood (or evidence) data for model comparison
performed in the 'twin' pipeline is shown in Table \ref{tab:evidence_twin}.
The best (that is, the one with the highest model weight)
candidate model assumes a JC nucleotide substitution model,
an RLN clock and a Yule tree model.
Note that there is a mismatch between the actual process of how the twin tree
and twin alignment are generated, as the twin tree is generated by a
BD process, and the alignment is simulated using a JC nucleotide
substitution model and a strict clock model.

>>>>

Based on the 'twin alignment' (center-right panel), the candidate model
with the highest marginal likelihood is determined, from the same 
set of 15 candidate models. The inference model that had the
highest evidence (as shown in Table \ref{tab:evidence_twin}) was 
the inference model with a JC nucleotide substitution model,
an RLN clock model and a Yule tree model 
\new{
  (Note that this is different from how the twin tree was generated which was with a BD process and the alignment
  was simulated with a JC substitution model and strict clock model
  ). However, the extinction rate used in simulating the twin tree was practically 0, thus resembling a Yule process.
}
From the 'twin alignment' this best candidate inference model is run.
The resulting posterior trees are shown in the fourth panel
of the third row of posteriors in figure \ref{fig:pipeline}.

@@

From the names of the estimated parameters, it is clear that
the best candidate model for the twin tree
is JC nucleotide substitution 
model (no parameter needed to be estimated),
an RLN clock model (which can be inferred from the parameter 'rate.mean') 
and a Yule model ('YuleModel', 'birthRate').
Note that there is a mismatch between the actual process of how the twin tree
and twin alignment are generated, as the twin tree is generated by a
BD process, and the alignment is simulated using a JC nucleotide
substitution model and a strict clock model. Again we note that the extinction rate used to simulate the twin tree (estimated from the true tree) was practically 0, so the BD process resembled a Yule process.

@@

The marginal likelihood (or evidence) data for model comparison
performed in the 'twin' pipeline is shown in Table \ref{tab:evidence_twin}.
The best (that is, the one with the highest model weight)
candidate model assumes a JC nucleotide substitution model,
an RLN clock and a Yule tree model.
Note that there is a mismatch between the actual process of how the twin tree
and twin alignment are generated, as the twin tree is generated by a
BD process, and the alignment is simulated using a JC nucleotide
substitution model and a strict clock model. The extinction rate in simulating the BD process (estimated from the true tree) was, however, practically 0, so the BD process resembled a Yule process.
